Summary of the Iberian Bees Database

### 2020-05-23 Summary.Rmd
Play with plotting.

---
title: "Summary of the Iberian Bees Database"
author: I. Bartomeus, T. Wood, L. Carvalheiro, C. Molina, et al. - 
date: "`r format(Sys.time(), '%d %B, %Y')`"
#output: pdf_document
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

We have records all over the peninsula, but higer concentrations are marked in red.

```{r echo=FALSE, message=FALSE, warning=FALSE}
#map
library(rgdal)
library(ggplot2)

@@

>>>>

---
title: "Summary of the Iberian Bees Database"
author: I. Bartomeus, T. Wood, L. Carvalheiro, C. Molina, et al. - 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
#output: github_document
editor_options: 
  chunk_output_type: console
---

@@

We have records all over the peninsula, but higer concentrations are marked in yellow.

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#map
library(rgdal)
library(ggplot2)

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
#code courtesi of Paco Rodriguez.
library(sf)
library(raster)
library(rasterVis)

crs.geo <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
crs.laea <- "+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs"

dat <- subset(data, !is.na(Latitude))
datos.sf <- st_as_sf(dat,
                     coords = c("Longitude", "Latitude"),
                     crs = crs.geo)

datos.laea <- st_transform(datos.sf,
                           crs = crs.laea)

ras <- raster(datos.laea, resolution = 10000)

ras.counts <- rasterize(datos.laea[, "accepted_name"], ras,
               field = "accepted_name", fun = "count")
str(datos.laea)
datos.laea$total <- datos.laea$Male + datos.laea$Female + datos.laea$Worker + datos.laea$Not.specified 
ras.counts2 <- rasterize(datos.laea[, "total"], ras,
               field = "total", fun = "sum")
ras2 <- raster(datos.laea, resolution = 30000)
ras.richness <- rasterize(datos.laea[, "accepted_name"], ras2,
               field = "accepted_name", fun = function(x, ...)
                 {length(unique(na.omit(x)))} )
library(vegan)
ras.chao <- rasterize(datos.laea[, "accepted_name"], ras2,
               field = "accepted_name", fun = function(x, ...)
                 {estimateR(t(as.matrix(x = table(x), nrow = 1, ncol = x)))[2,1]} ) #2 chao, 4 ACE #TO THIS WELL, We nees to recover abundances.

#levelplot(log(ras.counts+1), margin = FALSE, scales = list(draw = FALSE),
 #         par.settings = viridisTheme())
levelplot(log(ras.counts2+1), margin = FALSE, scales = list(draw = FALSE),
          par.settings = viridisTheme())
#levelplot(log(ras.richness+1), margin = FALSE, scales = list(draw = FALSE),
 #         par.settings = viridisTheme())
#levelplot(ras.chao, margin = FALSE, scales = list(draw = FALSE),
 #         par.settings = viridisTheme())

```
